---
title: "Alcohol vs Seat choice"
author: "Alma Andreasian"
date: "14 september 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

$H_0$ there is no difference in alcohol consumption based on where one sits in class.
$H_A$ There is a difference in alcohol consumption based on where one sits in class.

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```             

The box plot shows that the people in the back tend to consume more alcohole than the people that sit in the front.
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

people in the back tend to consume more alcohole than the people that sit in the front.
 
## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

```{r}
plot(TukeyHSD(model1))
```

First of all we got p- values of 0.000116  so we conclude we reject $H_0$; there is a difference in alcohol consumption based on where one sits.


## Conclusions

In conclusion the people who sit in the back consume more alcohol there is a slight difference in alcohol consumption than the people who sit in the middle front and the back.


